---
title: "Run Bayesian Models"
author: "Matthew Simonson"
date: "7/1/2022"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r}
rm(list=ls())
library(tidyverse)
library(data.table)
library(parallel)
library(brms)
library(texreg)
options(cores = detectCores())
run_main_effects <- TRUE
```

## Strings
```{r}
outcomes <- c("illegal_imm_prob_us",
              "illegal_imm_prob_cmty",
              "restrict_legal_imm",
              "partyid",
              "ideology",
              "obama_appr",
              "political_interest",
              "participation_index",
              "political_talk_with_family",
              "political_talk_with_friends")
```

## Load and Clean Data
```{r}
load("input_data/survey_data_new.RData")
```

Make binary versions of interaction variables and impute them forward
```{r}
survey_data[ Wave < 16.11 , republican := 1*(partyid > 4)]
survey_data[ Wave < 16.11 , conservative := 1*(ideology > 4)]
survey_data[ Wave < 16.11 , neurotic := 1*(neuroticism > 3)]
survey_data[ Wave < 16.11 , anxious := 1*(frequency_anxious > 2.5)]
mods <- c("republican","conservative","neurotic","anxious")
survey_data[, (mods) := nafill(.SD, "locf"), by=id, .SDcols=mods]
```

Binary versions for with other thresholds for robustness checks
```{r}
survey_data[ Wave < 16.11 , republican_3 := 1*(partyid > 3)]
survey_data[ Wave < 16.11 , conservative_3 := 1*(ideology > 3)]
survey_data[ Wave < 16.11 , neurotic_2 := 1*(neuroticism > 2)]
survey_data[ Wave < 16.11 , anxious_2 := 1*(frequency_anxious > 2)]

mods <- c("republican_3","conservative_3","neurotic_2","anxious_2")
survey_data[, (mods) := nafill(.SD, "locf"), by=id, .SDcols=mods]
```

```{r}
survey_data[ , republican_4:=republican]
survey_data[ , conservative_4:=conservative]
survey_data[ , neurotic_3:=neurotic]
survey_data[ , anxious_2.5:=anxious]
```

```{r}
survey_data[ Wave < 16.11 , republican_5 := 1*(partyid > 5)]
survey_data[ Wave < 16.11 , conservative_5 := 1*(ideology > 5)]
survey_data[ Wave < 16.11, neurotic_4 := 1*(neuroticism > 4)]
survey_data[ Wave < 16.11, anxious_3 := 1*(frequency_anxious > 3)]

mods <- c("republican_5","conservative_5","neurotic_4","anxious_3")
survey_data[, (mods) := nafill(.SD, "locf"), by=id, .SDcols=mods]
```

Preserve original variables
```{r}
survey_data[ , partyid.raw := partyid]
survey_data[ , ideology.raw := ideology]
survey_data[ , neuroticism.raw := neuroticism]
survey_data[ , frequency_anxious.raw := frequency_anxious]
```

Drop observations with no outcomes recorded
```{r}
dat17 <- survey_data[is.na(illegal_imm_prob_us) +
                 is.na(illegal_imm_prob_cmty) +
                 is.na(restrict_legal_imm) +
                 is.na(partyid) + 
                 is.na(ideology) +
                 is.na(obama_appr) +
                 is.na(political_interest) +
                 is.na(participation_index) + 
                 is.na(political_talk_with_family) + 
                 is.na(political_talk_with_friends) < 10]
```

Standardize outcomes
```{r}
dat17 <- sjmisc::std(dat17, outcomes, suffix = "")
```

Data subsets

```{r}
dat <- dat17[Wave<17]

dat.fd.tr  <- dat %>% filter(Wave %in% c(16.08, 16.11)) %>%
  mutate(wave_tr = 1*(Wave==16.11)) %>% 
  filter(chapter==12)

dat.fd.ctrl  <- dat %>% filter(Wave %in% c(16.08, 16.11)) %>%
  mutate(wave_tr = 1*(Wave==16.11)) %>% 
  filter(chapter!=12)
```

Save data
```{r}
save(dat, dat17, dat.fd.tr, dat.fd.ctrl, file = "input_data/use_this_data.Rdata")
```


# First Differences

## H1
```{r eval = run_main_effects}

set.seed(20015)
fdt.imm.us <- brm(illegal_imm_prob_us ~ wave_tr + ( 1 | id),
               data = dat.fd.tr[!is.na(illegal_imm_prob_us)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.imm.us <- brm(illegal_imm_prob_us ~ wave_tr + ( 1 | id),
               data = dat.fd.ctrl[!is.na(illegal_imm_prob_us)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```


```{r}

fdt.imm.cmty <- brm(illegal_imm_prob_cmty ~ wave_tr + ( 1 | id),
               data = dat.fd.tr[!is.na(illegal_imm_prob_cmty)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.imm.cmty <- brm(illegal_imm_prob_cmty ~ wave_tr + ( 1 | id),
               data = dat.fd.ctrl[!is.na(illegal_imm_prob_cmty)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```

```{r}

fdt.imm.legal <- brm(restrict_legal_imm ~ wave_tr + ( 1 | id),
               data = dat.fd.tr[!is.na(restrict_legal_imm)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.imm.legal <- brm(restrict_legal_imm ~ wave_tr + ( 1 | id),
               data = dat.fd.ctrl[!is.na(restrict_legal_imm)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

```

## H2

```{r}

fdt.party <- brm(partyid ~ wave_tr+ ( 1 | id),
               data = dat.fd.tr[!is.na(partyid)],
               seed = 20015,
               control = list(adapt_delta = .995),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.party <- brm(partyid ~ wave_tr+ ( 1 | id),
               data = dat.fd.ctrl[!is.na(partyid)],
               seed = 20015,
               control = list(adapt_delta = .995),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```

```{r}

fdt.ideo <- brm(ideology ~ wave_tr+ ( 1 | id),
               data = dat.fd.tr[!is.na(ideology)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.ideo <- brm(ideology ~ wave_tr+ ( 1 | id),
               data = dat.fd.ctrl[!is.na(ideology)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```

```{r}

fdt.obama <- brm(obama_appr ~ wave_tr+ ( 1 | id),
               data = dat.fd.tr[!is.na(obama_appr)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.obama <- brm(obama_appr ~ wave_tr+ ( 1 | id),
               data = dat.fd.ctrl[!is.na(obama_appr)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```
## H3
```{r}

fdt.particip <- brm(participation_index ~ wave_tr+ ( 1 | id),
               data = dat.fd.tr[!is.na(participation_index)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.particip <- brm(participation_index ~ wave_tr+ ( 1 | id),
               data = dat.fd.ctrl[!is.na(participation_index)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```

```{r}

fdt.int <- brm(political_interest ~ wave_tr+ ( 1 | id),
               data = dat.fd.tr[!is.na(political_interest)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.int <- brm(political_interest ~ wave_tr+ ( 1 | id),
               data = dat.fd.ctrl[!is.na(political_interest)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```

```{r}

fdt.tfam <- brm(political_talk_with_family ~ wave_tr+ ( 1 | id),
               data = dat.fd.tr[!is.na(political_talk_with_family)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.tfam <- brm(political_talk_with_family ~ wave_tr+ ( 1 | id),
               data = dat.fd.ctrl[!is.na(political_talk_with_family)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```



```{r}

fdt.tfr <- brm(political_talk_with_friends ~ wave_tr+ ( 1 | id),
               data = dat.fd.tr[!is.na(political_talk_with_friends)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)

fdc.tfr <- brm(political_talk_with_friends ~ wave_tr+ ( 1 | id),
               data = dat.fd.ctrl[!is.na(political_talk_with_friends)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```
```{r}

fdt_models_list <- list(fdt.imm.us, fdt.imm.cmty, fdt.imm.legal,
     fdt.party, fdt.ideo, fdt.obama,
     fdt.particip, fdt.int, fdt.tfam, fdt.tfr)
save(fdt_models_list, file = "model_objects/first_diff_treated.Rdata")
fdc_models_list <- list(fdc.imm.us, fdc.imm.cmty, fdc.imm.legal,
     fdc.party, fdc.ideo, fdc.obama,
     fdc.particip, fdc.int, fdc.tfam, fdc.tfr)
save(fdc_models_list, file = "model_objects/first_diff_control.Rdata")

```



# Main Effects
## H1
```{r eval = run_main_effects}
m.imm.us <- brm(illegal_imm_prob_us ~ tr + ( 1 | id) + (1|Wave),
               data = dat[!is.na(illegal_imm_prob_us)],
               seed = 20015,
               control = list(adapt_delta = .99),
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```

```{r eval = run_main_effects}
m.imm.cmty <- brm(illegal_imm_prob_cmty ~ tr + ( 1 | id) + (1|Wave),
             data = dat[!is.na(illegal_imm_prob_cmty)],
             seed = 20015,
             prior = set_prior("normal(0,2)", class = "b"),
             cores = 4)
```

```{r eval = run_main_effects}
m.imm.legal <- brm(restrict_legal_imm ~ tr + ( 1 | id) + (1|Wave),
                  data = dat[!is.na(restrict_legal_imm)],
                  seed = 20015,
                  prior = set_prior("normal(0,2)", class = "b"),
                  cores = 4)
```

## H2
```{r eval = run_main_effects}
m.party <- brm(partyid ~ tr + ( 1 | id) + (1|Wave),
               data = dat[!is.na(partyid)],
               seed = 20015, iter = 4000,
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```


```{r eval = run_main_effects}
m.ideo <- brm(ideology ~ tr + ( 1 | id) + (1|Wave),
              data = dat[!is.na(ideology)],
              seed = 20015,
              prior = set_prior("normal(0,2)", class = "b"),
              cores = 4)
```


```{r eval = run_main_effects}
m.obama <- brm(obama_appr ~ tr + ( 1 | id) + (1|Wave),
               data = dat[!is.na(obama_appr)],
               seed = 20015,
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```

## H3
```{r eval = run_main_effects}
m.particip <- brm(participation_index ~ tr + ( 1 | id) + (1|Wave),
               data = dat[!is.na(participation_index)],
               seed = 20015,
               prior = set_prior("normal(0,2)", class = "b"),
               cores = 4)
```


```{r eval = run_main_effects}
m.int <- brm(political_interest ~ tr + ( 1 | id) + (1|Wave),
                  data = dat[!is.na(political_interest)],
                  seed = 20015,
                  prior = set_prior("normal(0,2)", class = "b"),
                  cores = 4)
```


```{r eval = run_main_effects}
m.tfam <- brm(political_talk_with_family ~ tr + ( 1 | id) + (1|Wave),
              data = dat[ is.na(political_talk_with_family)==F],
              seed = 20015,
              control = list(adapt_delta = .99),
              prior = set_prior("normal(0,2)", class = "b"),
              cores = 4)
```


```{r eval = run_main_effects}
m.tfr <- brm(political_talk_with_friends ~ tr + ( 1 | id) + (1|Wave),
             data = dat[ is.na(political_talk_with_friends)==F],
             seed = 20015,
             control = list(adapt_delta = .99),
             prior = set_prior("normal(0,2)", class = "b"),
             cores = 4)
```


```{r}
main_models_list <- list(m.imm.us, m.imm.cmty, m.imm.legal,
     m.party, m.ideo, m.obama,
     m.particip, m.int, m.tfam, m.tfr)
save(main_models_list, file = "model_objects/main.Rdata")

```


# Interactions
## Republican

### H1/4
```{r eval=run_rep_interactions}
m.imm.usXrep <- brm(illegal_imm_prob_us ~ tr*republican + ( 1 | id) + (1|Wave),
                    data = dat[is.na(illegal_imm_prob_us)+is.na(republican)==0],
                    control = list(adapt_delta = .99),
                    seed = 20015,
                    prior = set_prior("normal(0,1)", class = "b"),
                    cores = 4)
```


```{r eval=run_rep_interactions}
m.imm.cmtyXrep <- brm(illegal_imm_prob_cmty ~ tr*republican + ( 1 | id) + (1|Wave),
                      data = dat[is.na(illegal_imm_prob_cmty)+ is.na(republican)==0],
                      control = list(adapt_delta = .99),
                      seed = 20015,
                      prior = set_prior("normal(0,1)", class = "b"),
                      cores = 4)
```


```{r eval=run_rep_interactions}
m.imm.legalXrep <- brm(restrict_legal_imm ~ tr*republican + ( 1 | id) + (1|Wave),
                       data = dat[is.na(restrict_legal_imm) + is.na(republican)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```

### H2/4
```{r eval=run_rep_interactions}
m.partyXrep <- brm(partyid ~ tr*republican + ( 1 | id) + (1|Wave),
                   data = dat[is.na(partyid) + is.na(republican)==0],
                   control = list(adapt_delta = .99),
                   seed = 20015,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=run_rep_interactions}
m.ideoXrep <- brm(ideology ~ tr*republican + ( 1 | id) + (1|Wave),
                  data = dat[is.na(ideology) + is.na(republican)==0],
                  control = list(adapt_delta = .99),
                  seed = 20015,
                  prior = set_prior("normal(0,1)", class = "b"),
                  cores = 4)
```


```{r eval=run_rep_interactions}
m.obamaXrep <- brm(obama_appr ~ tr*republican + ( 1 | id) + (1|Wave),
                   data = dat[is.na(obama_appr) + is.na(republican)==0],
                   control = list(adapt_delta = .99),
                   seed = 20015,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```
### H3/4

```{r eval=run_rep_interactions}
m.participXrep <- brm(participation_index ~ tr*republican + ( 1 | id) + (1|Wave),
                      data = dat[is.na(participation_index) + is.na(republican)==0],
                      control = list(adapt_delta = .99),
                      seed = 20015,
                      prior = set_prior("normal(0,1)", class = "b"),
                      cores = 4)
```


```{r eval=run_rep_interactions}
m.intXrep <- brm(political_interest ~ tr*republican + ( 1 | id) + (1|Wave),
                 data = dat[is.na(political_interest) + is.na(republican)==0],
                 control = list(adapt_delta = .99),
                 seed = 20015,
                 prior = set_prior("normal(0,1)", class = "b"),
                 cores = 4)
```


```{r eval=run_rep_interactions}
m.tfamXrep <- brm(political_talk_with_family ~ tr*republican + ( 1 | id) + (1|Wave),
                  data = dat[is.na(political_talk_with_family) + is.na(republican)==0],
                  control = list(adapt_delta = .99),
                  seed = 20015,
                  prior = set_prior("normal(0,1)", class = "b"),
                  cores = 4)
```


```{r eval=run_rep_interactions}
m.tfrXrep <- brm(political_talk_with_friends ~ tr*republican + ( 1 | id) + (1|Wave),
                 data = dat[is.na(political_talk_with_friends) + is.na(republican)==0],
                 control = list(adapt_delta = .99),
                 seed = 20015,
                 prior = set_prior("normal(0,1)", class = "b"),
                 cores = 4)
```


```{r eval=run_rep_interactions}
republican_models_list <- list(
        m.imm.usXrep, m.imm.cmtyXrep, m.imm.legalXrep,
     m.partyXrep, m.ideoXrep, m.obamaXrep,
     m.participXrep, m.intXrep, m.tfamXrep, m.tfrXrep
)
save(republican_models_list,
     file = "model_objects/interact_republican.Rdata")
```

## Conservative

### H1/4
```{r eval=run_con_interactions}
m.imm.usXcon <- brm(illegal_imm_prob_us ~ tr*conservative + ( 1 | id) + (1|Wave),
                    data = dat[is.na(illegal_imm_prob_us)+is.na(conservative)==0],
                    control = list(adapt_delta = .99),
                    seed = 20015,
                    prior = set_prior("normal(0,1)", class = "b"),
                    cores = 4)
```


```{r eval=run_con_interactions}
m.imm.cmtyXcon <- brm(illegal_imm_prob_cmty ~ tr*conservative + ( 1 | id) + (1|Wave),
                    data = dat[is.na(illegal_imm_prob_cmty)+ is.na(conservative)==0],
                    control = list(adapt_delta = .99),
                    seed = 20015,
                    prior = set_prior("normal(0,1)", class = "b"),
                    cores = 4)
```


```{r eval=run_con_interactions}
m.imm.legalXcon <- brm(restrict_legal_imm ~ tr*conservative + ( 1 | id) + (1|Wave),
                      data = dat[is.na(restrict_legal_imm) + is.na(conservative)==0],
                      control = list(adapt_delta = .99),
                      seed = 20015,
                      prior = set_prior("normal(0,1)", class = "b"),
                      cores = 4)
```

### H1/4

```{r eval=run_con_interactions}
m.partyXcon <- brm(partyid ~ tr*conservative + ( 1 | id) + (1|Wave),
                       data = dat[is.na(partyid) + is.na(conservative)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```
```{r eval=run_con_interactions}
m.ideoXcon <- brm(ideology ~ tr*conservative + ( 1 | id) + (1|Wave),
                       data = dat[is.na(ideology) + is.na(conservative)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```

```{r eval=run_con_interactions}
m.obamaXcon <- brm(obama_appr ~ tr*conservative + ( 1 | id) + (1|Wave),
                       data = dat[is.na(obama_appr) + is.na(conservative)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```

### H3/4
```{r eval=run_con_interactions}
m.participXcon <- brm(participation_index ~ tr*conservative + ( 1 | id) + (1|Wave),
                   data = dat[is.na(participation_index) + is.na(conservative)==0],
                   control = list(adapt_delta = .99),
                   seed = 20015,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=run_con_interactions}
m.intXcon <- brm(political_interest ~ tr*conservative + ( 1 | id) + (1|Wave),
                   data = dat[is.na(political_interest) + is.na(conservative)==0],
                   control = list(adapt_delta = .99),
                   seed = 20015,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=run_con_interactions}
m.tfamXcon <- brm(political_talk_with_family ~ tr*conservative + ( 1 | id) + (1|Wave),
                   data = dat[is.na(political_talk_with_family) + is.na(conservative)==0],
                   control = list(adapt_delta = .99),
                   seed = 20015,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=run_con_interactions}
m.tfrXcon <- brm(political_talk_with_friends ~ tr*conservative + ( 1 | id) + (1|Wave),
                   data = dat[is.na(political_talk_with_friends) + is.na(conservative)==0],
                   control = list(adapt_delta = .99),
                   seed = 20015,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=FALSE}

conservative_models_list <- 
        list(m.imm.usXcon, m.imm.cmtyXcon,
             m.imm.legalXcon,
             m.partyXcon, m.ideoXcon, m.obamaXcon,
             m.participXcon, m.intXcon, m.tfamXcon, m.tfrXcon)

save(conservative_models_list,
     file = "model_objects/interact_conservative.Rdata")
```

## Anxious
```{r eval=FALSE}
m.imm.usXanx <- brm(illegal_imm_prob_us ~ tr*anxious + ( 1 | id) + (1|Wave),
                    data = dat[is.na(illegal_imm_prob_us)+is.na(anxious)==0],
                    control = list(adapt_delta = .99),
                    seed = 20015,
                    prior = set_prior("normal(0,1)", class = "b"),
                    cores = 4)
```


```{r eval=FALSE}
m.imm.cmtyXanx <- brm(illegal_imm_prob_cmty ~ tr*anxious + ( 1 | id) + (1|Wave),
                    data = dat[is.na(illegal_imm_prob_cmty)+is.na(anxious)==0],
                    control = list(adapt_delta = .99),
                    seed = 20015,
                    prior = set_prior("normal(0,1)", class = "b"),
                    cores = 4)
```


```{r eval=FALSE}
m.imm.legalXanx <- brm(restrict_legal_imm ~ tr*anxious + ( 1 | id) + (1|Wave),
                     data = dat[is.na(restrict_legal_imm)+is.na(anxious)==0],
                     control = list(adapt_delta = .99),
                     seed = 20015,
                     prior = set_prior("normal(0,1)", class = "b"),
                     cores = 4)
```


```{r eval=FALSE}
m.partyXanx <- brm(partyid ~ tr*anxious + ( 1 | id) + (1|Wave),
                       data = dat[is.na(partyid)+is.na(anxious)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015, iter = 5000,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.ideoXanx <- brm(ideology ~ tr*anxious + ( 1 | id) + (1|Wave),
                       data = dat[is.na(ideology)+is.na(anxious)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015, iter = 4000,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.obamaXanx <- brm(obama_appr ~ tr*anxious + ( 1 | id) + (1|Wave),
                       data = dat[is.na(obama_appr)+is.na(anxious)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.participXanx <- brm(participation_index ~ tr*anxious + ( 1 | id) + (1|Wave),
                       data = dat[is.na(participation_index)+is.na(anxious)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.intXanx <- brm(political_interest ~ tr*anxious + ( 1 | id) + (1|Wave),
                       data = dat[is.na(political_interest)+is.na(anxious)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.tfamXanx <- brm(political_talk_with_family ~ tr*anxious + ( 1 | id) + (1|Wave),
                       data = dat[is.na(political_talk_with_family)+is.na(anxious)==0],
                       control = list(adapt_delta = .995),
                       seed = 20015, iter = 5000,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.tfrXanx <- brm(political_talk_with_friends ~ tr*anxious + ( 1 | id) + (1|Wave),
                       data = dat[is.na(political_talk_with_friends)+is.na(anxious)==0],
                       control = list(adapt_delta = .99),
                       seed = 20015,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
anxious_models_list <- list(
        m.imm.usXanx, m.imm.cmtyXanx, m.imm.legalXanx,
     m.partyXanx, m.ideoXanx, m.obamaXanx,
     m.participXanx, m.intXanx, m.tfamXanx, m.tfrXanx
)
save(anxious_models_list,
     file = "model_objects/interact_anxiety.Rdata")
```

## Neurotic

```{r eval=FALSE}
m.imm.usXneu <- brm(illegal_imm_prob_us ~ tr*neurotic + ( 1 | id) + (1|Wave),
                    data = dat[is.na(illegal_imm_prob_us)+is.na(neurotic)==0],
                    control = list(adapt_delta = .99),
                    seed = 19104,
                    prior = set_prior("normal(0,1)", class = "b"),
                    cores = 4)
```


```{r eval=FALSE}
m.imm.cmtyXneu <- brm(illegal_imm_prob_cmty ~ tr*neurotic + ( 1 | id) + (1|Wave),
                    data = dat[is.na(illegal_imm_prob_cmty) + is.na(neurotic)==0],
                    control = list(adapt_delta = .99),
                    seed = 19104,
                    prior = set_prior("normal(0,1)", class = "b"),
                    cores = 4)
```


```{r eval=FALSE}
m.imm.legalXneu <- brm(restrict_legal_imm ~ tr*neurotic + ( 1 | id) + (1|Wave),
                      data = dat[is.na(restrict_legal_imm) + is.na(neurotic)==0],
                      control = list(adapt_delta = .99),
                      seed = 19104,
                      prior = set_prior("normal(0,1)", class = "b"),
                      cores = 4)
```


```{r eval=FALSE}
m.ideoXneu <- brm(ideology ~ tr*neurotic + ( 1 | id) + (1|Wave),
                  data = dat[is.na(ideology) + is.na(neurotic)==0],
                  control = list(adapt_delta = .99),
                  seed = 19104,
                  prior = set_prior("normal(0,0.5)", class = "b"),
                  cores = 4)
```


```{r eval=FALSE}
m.partyXneu <- brm(partyid ~ tr*neurotic + ( 1 | id) + (1|Wave),
                       data = dat[is.na(partyid) + is.na(neurotic)==0],
                       control = list(adapt_delta = .99),
                       seed = 19104,
                       prior = set_prior("normal(0,0.5)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.obamaXneu <- brm(obama_appr ~ tr*neurotic + ( 1 | id) + (1|Wave),
                       data = dat[is.na(obama_appr) + is.na(neurotic)==0],
                       control = list(adapt_delta = .99),
                       seed = 19104,
                       prior = set_prior("normal(0,1)", class = "b"),
                       cores = 4)
```


```{r eval=FALSE}
m.participXneu <- brm(participation_index ~ tr*neurotic + ( 1 | id) + (1|Wave),
                   data = dat[is.na(participation_index) + is.na(neurotic)==0],
                   control = list(adapt_delta = .99),
                   seed = 19104,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=FALSE}
m.intXneu <- brm(political_interest ~ tr*neurotic + ( 1 | id) + (1|Wave),
                   data = dat[is.na(political_interest) + is.na(neurotic)==0],
                   control = list(adapt_delta = .99),
                   seed = 19104,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=FALSE}
m.tfamXneu <- brm(political_talk_with_family ~ tr*neurotic + ( 1 | id) + (1|Wave),
                   data = dat[is.na(political_talk_with_family) + is.na(neurotic)==0],
                   control = list(adapt_delta = .99),
                   seed = 19104,
                   prior = set_prior("normal(0,1)", class = "b"),
                   cores = 4)
```


```{r eval=FALSE}
m.tfrXneu <- brm(political_talk_with_friends ~ tr*neurotic + ( 1 | id) + (1|Wave),
                   data = dat[is.na(political_talk_with_friends) + is.na(neurotic)==0],
                   control = list(adapt_delta = .99),
                   seed = 19104,
                   prior = set_prior("normal(0,0.5)", class = "b"),
                   cores = 4)
```


```{r eval=FALSE}
neurotic_models_list <- list(m.imm.usXneu, m.imm.cmtyXneu, m.imm.legalXneu,
     m.partyXneu, m.ideoXneu, m.obamaXneu,
     m.participXneu, m.intXneu, m.tfamXneu, m.tfrXneu)
save(neurotic_models_list,
     file = "model_objects/interact_neurotic.Rdata")
```

## Save



```{r echo=FALSE}

# 
# save(m.imm.usXrep,m.imm.usXcon, m.imm.usXneu, m.imm.usXstress, file = "model_objects/bayes_interactions_us.Rdata" )
# save(m.imm.cmtyXrep,m.imm.cmtyXcon, m.imm.cmtyXneu, m.imm.cmtyXstress, file = "model_objects/bayes_interactions_cmty.Rdata" )
# save(m.imm.legalXrep,m.imm.legalXcon, m.imm.legalXneu, m.imm.legalXstress, file = "model_objects/bayes_interactions_legal.Rdata" )
# save(m.ideoXrep,m.ideoXcon, m.ideoXneu, m.ideoXstress, file = "model_objects/bayes_interactions_ideo.Rdata" )
# save(m.partyXrep,m.partyXcon, m.partyXneu, m.partyXstress, file = "model_objects/bayes_interactions_party.Rdata" )
# save(m.obamaXrep,m.obamaXcon, m.obamaXneu, m.obamaXstress, file = "model_objects/bayes_interactions_obama.Rdata" )
# save(m.participXrep,m.participXcon, m.participXneu, m.participXstress, file = "model_objects/bayes_interactions_particip.Rdata" )
# save(m.intXrep,m.intXcon, m.intXneu, m.intXstress, file = "model_objects/bayes_interactions_int.Rdata" )
# save(m.tfrXrep,m.tfrXcon, m.tfrXneu, m.tfrXstress, file = "model_objects/bayes_interactions_tfr.Rdata" )
# save(m.tfamXrep,m.tfamXcon, m.tfamXneu, m.tfamXstress, file = "model_objects/bayes_interactions_tfam.Rdata" )

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
