---
title: "Terrorism Replication"
author: "Matthew Simonson"
date: "7/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup
### Packages
```{r, echo=F}
cat("\14")
rm(list = ls())
library(tidyverse)
#library(ggplot2)
#library(forcats)
#library(purrr)
library(data.table)
library(parameters)
library(viridisLite)
library(bayestestR)
library(insight)
library(emmeans)
library(fixest)
#library(modelsummary)
library(sjPlot)
library(gtsummary)
#library(gt)
#library(texreg)
library(parallel)
library(kableExtra)
library(brms)
```

### Settings
```{r}
setFixest_fml(..outcomes = ~c(illegal_imm_prob_us,
                              illegal_imm_prob_cmty,
                              restrict_legal_imm,
                              partyid,
                              ideology,
                              obama_appr,
                              political_interest,
                              participation_index,
                              political_talk_with_family,
                              political_talk_with_friends),
              
              ..outcomes17 = ~c(illegal_imm_prob_us,
                              illegal_imm_prob_cmty,
                              #restrict_legal_imm,
                              partyid,
                              ideology,
                              #obama_appr,
                              political_interest,
                              participation_index,
                              political_talk_with_family,
                              political_talk_with_friends))

setFixest_dict(c("tr" = "treatment",
                 "illegal_imm_prob_us" = "illegal imm us",
                 "illegal_imm_prob_cmty" = "illegal imm cmty",
                 "restrict_legal_imm" = "legal imm",
                 "obama_appr" = "obama",
                 "partyid" = "party",
                 "political_interest" = "interest",
                 "participation_index" = "participation",
                 "political_talk_with_family" = "talk family",
                 "political_talk_with_friends" = "talk friends",
                 "republican_3" = "Republican",
                 "republican" = "Republican",
                 "republican_5" = "Republican",
                 "conservative_3" = "conservative",
                 "conservative" = "conservative",
                 "conservative_5" = "conservative"
                 ))
setFixest_etable(digits = 2, digits.stats = 3)
```


### Load

```{r}
load("input_data/use_this_data.Rdata")
```

### Functions

```{r}

extract_brms_stats <- function(mod){
  draws <- get_parameters(mod)
  mp <- model_parameters(draws, ci_method = "hdi", as_draws = T, rope_ci = 1)
  hdi90 <- hdi(draws, component = "all", ci=.9)
  ess <- effective_sample(mod,component = "all")
  
  message("stats extracted!")
  
  tibble(mp) %>%
    rename(CI_low_95 = CI_low, CI_high_95 = CI_high) %>%
    left_join(ess, by = "Parameter") %>% 
    left_join(hdi90, by = "Parameter") %>%
    select(-CI) %>%
    rename(CI_low_90 = CI_low, CI_high_90 = CI_high) %>%
    mutate(rhat = rhat(mod)[Parameter],
           Parameter = Parameter %>% 
             gsub(pattern = "b_", replacement = "", fixed = T) %>% 
             gsub(pattern = "Intercept",replacement = "(intercept)", 
                  fixed = T) )
}


prep_brms_table <- function(stats_df){
  stats_df %>% 
    mutate(`90% HDI` = sprintf("(%.2f, %.2f)", CI_low_90, CI_high_90),
           `95% HDI` = sprintf("(%.2f, %.2f)", CI_low_95, CI_high_95),
           Parameter = Parameter %>% 
             gsub(pattern = "^tr", replacement = "treatment")) %>%
    relocate(`95% HDI`,
             `90% HDI`, 
             .after = "Median") %>%
    select(-starts_with("CI"), 
           -contains(c("ROPE")))
}

make_contrast_rep <- function(x) {
  contrast <- emmeans(x, ~ tr*republican) %>%
    pairs(by = "republican", reverse = T)
  
  message("marginal means calculated!")
    
  left_join(
    as.data.frame(contrast) %>% 
      rename(CI_low_95 = lower.HPD,
             CI_high_95 = upper.HPD),
    confint(contrast, level=.9) %>% 
      as.data.frame() %>%
      rename(CI_low_90 = lower.HPD,
             CI_high_90 = upper.HPD),
    by = c("contrast", "republican", "estimate"))
}

make_contrast_con <- function(x) {
  contrast <- emmeans(x, ~ tr*conservative) %>%
    pairs(by = "conservative", reverse = T)
  
  message("marginal means calculated!")
    
  left_join(
    as.data.frame(contrast) %>% 
      rename(CI_low_95 = lower.HPD,
             CI_high_95 = upper.HPD),
    confint(contrast, level=.9) %>% 
      as.data.frame() %>%
      rename(CI_low_90 = lower.HPD,
             CI_high_90 = upper.HPD),
    by = c("contrast", "conservative", "estimate"))
}
```

### Strings
```{r}
outcome_labels <-
  c("illegal immigration\nproblem in US",
    "illegal immigration\nproblem in community",
    "restrict\nlegal immigration",
    "party\n(Dem.–Rep. scale)",
    "ideology\n(Lib.–Con. scale)",
    "Obama approval",
    "political participation",
    "interest in politics",
    "discuss politics\nand current events\nwith family",
    "discuss politics\nand current events\nwith friends") %>%
  fct_inorder() %>% fct_rev()

hypothesis_labels <-
  c(rep("H1: Nativist Backlash",3),
    rep("H2: Righward Shift",3),
    rep("H3: Political Engagement", 4)) %>% fct_inorder()

political_labels <- c("not Republican (left)\nnot conservative (right)","Republican (left)\nConservative (right)")

fe_headers <- list("^Hypothesis:" = list("H1: Nativist Backlash" = 3, 
                                        "H2: Righward Shift" = 3, 
                                        "H3: Political Engagement" = 4))

fe_headers_april <- list("^Hypothesis:" = list("H1: Nativist Backlash" = 2, 
                                        "H2: Righward Shift" = 2, 
                                        "H3: Political Engagement" = 4))

section_headings <- rep(3, 10)
names(section_headings) <- 
  paste("Outcome:", outcome_labels %>% 
          gsub(pattern = "\n", replacement = " "))

section_headings_interact <- rep(5, 10)
names(section_headings_interact) <- 
  paste("Outcome:", outcome_labels %>% 
          gsub(pattern = "\n", replacement = " "))

section_headings_contrast <- rep(2, 10)
names(section_headings_contrast) <- 
  paste("Outcome:", outcome_labels %>% 
          gsub(pattern = "\n", replacement = " "))

first_diff_cap <- "Models for %s students comparing pre- and post-attack outcomes (%s)"

party_cap <- "%s models with party interactions (Republican defined as %d or higher where 1 is `strong Democrat' and 7 is `strong Republican')"
ideo_cap <- "%s models with ideology interactions (conservative defined as %d or higher where 1 is `extremely liberal' and 7 is `extremely conservative')"

```

## Descriptive Statistics

```{r}
d <- dat %>% 
  mutate(gender = factor(ifelse(gender==1, "male", "female")),
         location = factor(ifelse(chapter!=12, "non-local", "local")) %>% relevel("non-local"),
         period =  factor(ifelse(Wave!=16.11, "pre-attack", "post-attack")) %>% relevel("pre-attack"),
         zip_prop_us_born = us_born_population/total_population,
         zip_median_income = zip_median_income/1000,
         race = recode_factor(race,
                              black = "Black",
                              white = "White",
                              other = "Other"),
         immigration_status = gsub(x = immigration_status, 
                                   pattern = "scholar", 
                                   replacement = "student"),
         religion  = recode_factor(religion,
                                   Catholic = "Catholic",
                                   Protestant_etc = "Other Christian",
                                   Other = "Other Religion",
                                   None = "None"),
         first_gen = case_when(father_education > 4 & mother_education > 4 ~ "both",
                               mother_education > 4 | mother_education > 4~ "one",
                               father_education <= 4 | mother_education <= 4 ~ "neither") %>% fct_relevel("both", "one")
  ) %>% select(location, Wave,
               period,
               gender, 
               race, 
               religion, 
               immigration_status,
               first_gen,
               illegal_imm_prob_us, 
               illegal_imm_prob_cmty, 
               restrict_legal_imm,
               partyid, ideology, 
               obama_appr, 
               political_interest, 
               participation_index, 
               political_talk_with_family,    
               political_talk_with_friends,
               zip_median_income,
               zip_prop_us_born, candidate_choice, openness, extroversion, conscientiousness, neuroticism, agreeableness, stress_amount, happiness)

```

```{r}
tab_a1 <- d %>% 
  select(#location,
  gender, race, religion, 
  immigration_status, first_gen, 
  zip_median_income, zip_prop_us_born, candidate_choice, 
  #openness, extroversion, conscientiousness, neuroticism, agreeableness
) %>%
  tbl_summary(statistic = list(all_continuous() ~ "{median}", 
                               all_categorical() ~ "{p}%"),
              #by = location,
              # type = list(
              #   agreeableness ~ "continuous",
              #   neuroticism ~ "continuous",
              #   extroversion ~ "continuous",
              #   conscientiousness ~ "continuous",
              #   openness ~ "continuous"),
              label = list(
                zip_median_income ~ "median income in home ZIP ($1000s)",
                zip_prop_us_born ~ "proportion US-born pop. in home ZIP ",
                immigration_status ~ "immigration status",
                candidate_choice ~ "candidate choice",
                first_gen ~ "Parents' with Bachelor's deg."
              ),
              missing = "no")

# View
v <- tab_a1 %>% 
  as_kable_extra(
    digits = 1, 
    caption = "Descriptive statistics for students in residential scholarship program") %>%
  kable_styling(latex_options = "hold_position", font_size = 9)

# latex
l <- tab_a1 %>%
  as_kable_extra(format = "latex",
    digits = 1, 
    linesep = "",
    booktabs = T,
    caption = "Descriptive statistics for outcome variables",  
    label = "descriptives_cat") %>%
  kable_styling(latex_options = "HOLD_position",
                font_size = 9) %>% 
  gsub(pattern = "\\textsuperscript{1} %; Median", replacement = "Note: Statistics without a % are medians.\\Statistics based on observations. Students are counted multiple times if they appear in multiple waves.", fixed = T)

write(l, file="SI/table_descriptives_cat.tex")
```

```{r}
tab_a2 <- d %>%
  select(period, 
         location, 
         illegal_imm_prob_us, 
         illegal_imm_prob_cmty, 
         restrict_legal_imm,
         partyid, 
         ideology, 
         obama_appr, 
         political_interest, 
         participation_index, 
         political_talk_with_family,    
         political_talk_with_friends) %>%
  tbl_strata(
    strata = location,
    .tbl_fun =
      ~ .x %>%
  tbl_summary(statistic = list(all_continuous() ~ "{mean}"),
              by = period,
              type = list(
                illegal_imm_prob_us ~ "continuous",
                illegal_imm_prob_cmty ~ "continuous",
                restrict_legal_imm ~ "continuous",
                partyid ~    "continuous",
                ideology ~ "continuous",
                obama_appr ~ "continuous",
                participation_index ~ "continuous",
                political_interest ~ "continuous",
                political_talk_with_family ~ "continuous",
                political_talk_with_friends ~ "continuous"),
              label = list(
                illegal_imm_prob_us ~ "illegal imm US",
                illegal_imm_prob_cmty ~ "illegal imm cmty",
                restrict_legal_imm ~ "legal imm",
                partyid ~    "party",
                ideology ~ "ideology",
                obama_appr ~ "Obama",
                participation_index ~ "participation",
                political_interest ~ "interest",
                political_talk_with_family ~ "talk family",
                political_talk_with_friends ~ "talk friends"
              ),
              missing = "no")
  )

# View
v <- tab_a2 %>% 
  as_kable_extra(
    digits = 1, 
    caption = "Descriptive statistics for outcome variables") %>%
  kable_styling(latex_options = "hold_position", font_size = 9)

# latex
l <- tab_a2 %>%
  as_kable_extra(format = "latex",
    digits = 1, 
    linesep = "",
    booktabs = T,
    caption = "Descriptive statistics for outcome variables",  
    label = "descriptives") %>%
  kable_styling(latex_options = "HOLD_position",
                font_size = 9) %>% 
  gsub(pattern = "\\textsuperscript{1} Mean", replacement = "", fixed = T)

write(l, file="SI/table_descriptives.tex")
```

## Bayesian

### First differences

```{r}

load("model_objects/first_diff_treated.Rdata")

treat.first.diff.bayes.stats <- lapply(fdt_models_list, extract_brms_stats) %>%
  rbindlist() %>% 
  mutate(Hypothesis = rep(hypothesis_labels, each = 3))


table_treat_first_diff_bayes <- treat.first.diff.bayes.stats %>% 
  prep_brms_table() %>%
  mutate(Parameter = Parameter %>% gsub(pattern = "wave_tr", replacement = "Nov 2016 - Aug 2016")) %>%
  kbl(format = "latex",
    digits = 2, 
    booktabs = T,
    caption = sprintf(first_diff_cap, "local", "Bayesian"),
    label = "treat_fd") %>%
  kable_styling( latex_options = "hold_position",
                 font_size = 9)  %>%
  row_spec(3*(1:10)-1, bold = T) %>%
  pack_rows(index=section_headings, bold = T, hline_after = T)

write(table_treat_first_diff_bayes, file="SI/table_first_diff_bayes_tr.tex")
```

```{r}
load("model_objects/first_diff_control.Rdata")

ctrl.first.diff.bayes.stats <- lapply(fdc_models_list, extract_brms_stats) %>%
  rbindlist() %>% 
  mutate(Hypothesis = rep(hypothesis_labels, each = 3))

table_ctrl_first_diff_bayes <- ctrl.first.diff.bayes.stats %>% 
  prep_brms_table() %>%
  mutate(Parameter = Parameter %>% gsub(pattern = "wave_tr", replacement = "Nov 2016 - Aug 2016")) %>%
  kbl(format = "latex",
    digits = 2, 
    booktabs = T,
    caption = sprintf(first_diff_cap, "non-local", "Bayesian"),
    label = "ctrl_fd") %>%
  kable_styling( latex_options = "hold_position",
                 font_size = 9)  %>%
  row_spec(3*(1:10)-1, bold = T) %>%
  pack_rows(index=section_headings, bold = T, hline_after = T)

write(table_ctrl_first_diff_bayes, file="SI/table_first_diff_bayes_ctrl.tex")
```

Create tibble for plotting
```{r}
plt.tab.FD.bayes <- bind_rows(`non-local` = ctrl.first.diff.bayes.stats,
          `local` = treat.first.diff.bayes.stats, .id = "Location") %>%
  filter(Parameter == "wave_tr") %>%
  mutate(Outcome = rep(outcome_labels,2), 
         Hypothesis = rep(hypothesis_labels,2)) %>%
  rename(estimate = Median)

```



### Main

Load and analyze
```{r}
load("model_objects/main.Rdata")

main.bayes.stats <- lapply(main_models_list, extract_brms_stats) %>%
  rbindlist() %>% 
  mutate(Hypothesis = rep(hypothesis_labels, each = 3))
```

Create latex table for SI
```{r}
table_main_bayes <- main.bayes.stats %>% 
  prep_brms_table() %>%
  kbl(format = "latex",
    digits = 2, 
    booktabs = T,
    caption = "Main models (Bayesian)",
    label = "bayes_main") %>%
  kable_styling( latex_options = "hold_position",
                 font_size = 9)  %>%
  row_spec(3*(1:10)-1, bold = T) %>%
  pack_rows(index=section_headings, bold = T, hline_after = T)

write(table_main_bayes, file="SI/table_main_bayes.tex")
```

Create tibble for plotting
```{r}
plt.tab.bayes <- main.bayes.stats %>% filter(Parameter == "tr") %>%
  mutate(Outcome = outcome_labels, 
         Hypothesis = hypothesis_labels,
         Model = "Main") %>%
  rename(estimate = Median)
```

### Subgroup
#### party

Load and analyze
```{r}
load("model_objects/interact_republican.Rdata")

party.bayes.stats <- lapply(republican_models_list, 
                            extract_brms_stats) %>%
  rbindlist() %>% 
  mutate(Hypothesis = rep(hypothesis_labels, each = 5))
```

Create latex table for SI
```{r}
table_party_bayes <- party.bayes.stats %>% 
  prep_brms_table() %>%
  kbl(format = "latex",
    digits = 2, 
    booktabs = T,
    caption = sprintf(party_cap, "Bayesian", 4),
    label = "bayes_party") %>%
  kable_styling( latex_options = "hold_position",
                 font_size = 9)  %>%
  row_spec(5*(1:10)-1, bold = T) %>%
  pack_rows(index=section_headings_interact, bold = T, hline_after = T)

write(table_party_bayes, file="SI/table_party_bayes.tex")
```

Create table for plotting
```{r}
rep.tab <- lapply(republican_models_list, make_contrast_rep)

plt.tab.rep <- rbindlist(rep.tab)
plt.tab.rep[, Outcome := rep(outcome_labels, each = 2)]
```

and for SI
```{r Republican}
table_party_contrasts <- plt.tab.rep %>%
  mutate(Party = ifelse(republican==1, "Republican", "Not Republican")) %>%
  select(-contrast, -republican, -Outcome) %>%
  rename(Median = estimate,
         `Lower 95% HDI`= CI_low_90,
         `Upper 95% HDI`= CI_high_90,
         `Lower 90% HDI`= CI_low_95,
         `Upper 90% HDI`= CI_high_95) %>%
    relocate(Party) %>% 
kbl(format = "latex",
    digits = 2, 
    booktabs = T,
    caption = "Conditional treatment effects by party used to construct Figure 2, left panel",
    label = "constrast_party") %>%
  kable_styling( latex_options = "hold_position",
                 font_size = 9) %>%
  pack_rows(index = section_headings_contrast)

write(table_party_contrasts, file="SI/table_party_contrasts.tex")
```


#### ideology

Load and analyze
```{r}
load("model_objects/interact_conservative.Rdata")

ideo.bayes.stats <- lapply(conservative_models_list, extract_brms_stats) %>%
  rbindlist() %>% 
  mutate(Hypothesis = rep(hypothesis_labels, each = 5))
```

Create latex table for SI
```{r}
table_ideo_bayes <- ideo.bayes.stats %>% 
  prep_brms_table() %>%
  kbl(format = "latex",
    digits = 2, 
    booktabs = T,
    caption = sprintf(ideo_cap, "Bayesian", 4),
    label = "bayes_ideo") %>%
  kable_styling( latex_options = "hold_position",
                 font_size = 9)  %>%
  row_spec(5*(1:10)-1, bold = T) %>%
  pack_rows(index=section_headings_interact, bold = T, hline_after = T)

write(table_ideo_bayes, file="SI/table_ideo_bayes.tex")
```

Create tibble for plotting
```{r}
con.tab <- lapply(conservative_models_list, make_contrast_con)

plt.tab.con <- rbindlist(con.tab)
plt.tab.con[, Outcome := rep(outcome_labels, each = 2)]
```

and for SI
```{r}
table_ideo_contrasts <- plt.tab.con %>%
  mutate(Ideology = ifelse(conservative==1, "Conservative", "Not Conservative")) %>%
  select(-contrast, -conservative, -Outcome) %>%
  rename(Median = estimate,
         `Lower 95% HDI`= CI_low_90,
         `Upper 95% HDI`= CI_high_90,
         `Lower 90% HDI`= CI_low_95,
         `Upper 90% HDI`= CI_high_95) %>%
    relocate(Ideology) %>% 
kbl(format = "latex",
    digits = 2, 
    booktabs = T,
    caption = "Conditional treatment effects by ideology used to construct Figure 2, right panel",
    label = "constrast_ideo") %>%
  kable_styling( latex_options = "hold_position",
                 font_size = 9) %>%
  pack_rows(index = section_headings_contrast)

write(table_ideo_contrasts, file="SI/table_ideo_contrasts.tex")
```


## Fixed Effects

### First Differences

```{r}
m.tr <- dat.fd.tr %>%
  feglm(..outcomes ~ wave_tr |  id, data = .)


etable(m.tr, replace =T, file = "SI/table_first_diff_FE_tr.tex", 
       headers = fe_headers, 
       label = "tab:first_diff_FE_ctrl", 
       title = sprintf(first_diff_cap, "local", "frequentist"))


m.ctrl <- dat.fd.ctrl %>%
  feglm(..outcomes ~ wave_tr |  id, data = .)

etable(m.ctrl, replace =T, file = "SI/table_first_diff_FE_ctrl.tex", 
       headers = fe_headers, 
       label = "tab:first_diff_FE_tr", 
       title = sprintf(first_diff_cap, "non-local", "frequentist"))
```



### Main
```{r FE}
m <- feglm(..outcomes ~ tr  | Wave + id, data = dat, vcov = "twoway")

plt.tab.freq <- coefplot(m, only.params=T)[[1]] %>%
  rename(CI_low_95=ci_low, CI_high_95=ci_high) %>%
  bind_cols(
    coefplot(m, only.params=T, ci_level = 0.9)[[1]] %>%
      transmute(CI_low_90=ci_low, CI_high_90=ci_high)
  ) %>%
  mutate(Outcome = outcome_labels, Hypothesis = hypothesis_labels)

etable(m, replace =T, file = "SI/table_main_FE.tex", 
       headers = fe_headers, 
       label = "tab:main_FE", 
       title = "Main models (frequentist)")
```

### Robustness Checks
```{r Same State}
m <- feglm(..outcomes ~ tr  | Wave + id, data = dat[chapter %in% c(5,12)], vcov = "twoway")

plt.tab.freq.same.st <- coefplot(m, only.params=T)[[1]] %>% 
    rename(CI_low_95=ci_low, CI_high_95=ci_high) %>%
  bind_cols(
    coefplot(m, only.params=T, ci_level = 0.9)[[1]] %>% 
      transmute(CI_low_90=ci_low, CI_high_90=ci_high)
  ) %>% 
  mutate(Outcome = outcome_labels, Hypothesis = hypothesis_labels)



etable(m, replace =T, file = "SI/table_rob_same_state.tex", 
       headers = fe_headers, 
       label = "tab:same_state", 
       title = "Same-State Effects: Subsetting on respondents in the same state as the attack (frequentist)")

```

```{r Same School Year}
m <- feglm(..outcomes ~ tr  | Wave + id, data = dat[Wave > 16.05], vcov = "twoway")
plt.tab.freq.same.yr <- coefplot(m, only.params=T)[[1]] %>% 
    rename(CI_low_95=ci_low, CI_high_95=ci_high) %>%
  bind_cols(
    coefplot(m, only.params=T, ci_level = 0.9)[[1]] %>% 
      transmute(CI_low_90=ci_low, CI_high_90=ci_high)
  ) %>% 
  mutate(Outcome = outcome_labels, Hypothesis = hypothesis_labels)


etable(m, replace =T, file = "SI/table_rob_same_year.tex", 
       headers = fe_headers, 
       label = "tab:same_year", 
       title = "Same-Year Effects: Subsetting on observations in the same school year as the attack (frequentist)")
```

```{r Second Post Wave}

m <- feglm(..outcomes17 ~ tr  | Wave + id, data = dat17[Wave!=16.11], vcov = "twoway")

plt.tab.freq.17 <- coefplot(m, only.params=T)[[1]] %>% 
    rename(CI_low_95=ci_low, CI_high_95=ci_high) %>%
  bind_cols(
    coefplot(m, only.params=T, ci_level = 0.9)[[1]] %>% 
      transmute(CI_low_90=ci_low, CI_high_90=ci_high)
  ) %>% 
  mutate(Outcome = outcome_labels[-c(3,6)], Hypothesis = hypothesis_labels[-c(3,6)])

etable(m, replace =T, file = "SI/table_rob_long_term.tex", 
       headers = fe_headers_april, 
       label = "tab:long_term", tpt =T,
       notes = "Note: The Obama approval and legal immigration questions were not asked in this survey wave.",
       title = "Long-term effects: November 2016 post-treatment observations replaced with April 2017 observations (frequentist)")

```

```{r}
plt.tab.rob <- bind_rows(
  "Main" = plt.tab.freq,
  "Same State" = plt.tab.freq.same.st,
  "Same Year" = plt.tab.freq.same.yr,
  #"Two" = plt.tab.freq.1617,
  "Long-term" = plt.tab.freq.17, .id = "Model"
)
```


### Subgroup

#### party
```{r}
m <- feglm(..outcomes ~ tr*republican_3 | Wave + id, data = dat, vcov = "twoway")

etable(m, replace =T, file = "SI/table_rep_3.tex", 
       headers = fe_headers, 
       label = "tab:rep_3",
       title = sprintf(party_cap, "Frequentist", 4))

m <- feglm(..outcomes ~ tr*republican_3 | Wave + id, data = dat, vcov = "twoway")

etable(m, replace =T, file = "SI/table_rep_4.tex", 
       headers = fe_headers, 
       label = "tab:rep_4",
       title = sprintf(party_cap, "Frequentist", 5))

m <- feglm(..outcomes ~ tr*republican_3 | Wave + id, data = dat, vcov = "twoway")

etable(m, replace =T, file = "SI/table_rep_5.tex", 
       headers = fe_headers, 
       label = "tab:rep_5",
       title = sprintf(party_cap, "Frequentist", 6))
```

#### ideology

```{r}
m <- feglm(..outcomes ~ tr*conservative_3 | Wave + id, data = dat, vcov = "twoway")

etable(m, replace =T, file = "SI/table_con_3.tex", 
       headers = fe_headers, 
       label = "tab:con_3",
       title = sprintf(ideo_cap, "Frequentist", 4))

m <- feglm(..outcomes ~ tr*conservative_3 | Wave + id, data = dat, vcov = "twoway")

etable(m, replace =T, file = "SI/table_con_4.tex", 
       headers = fe_headers, 
       label = "tab:con_4",
       title = sprintf(ideo_cap, "Frequentist", 5))

m <- feglm(..outcomes ~ tr*conservative_3 | Wave + id, data = dat, vcov = "twoway")

etable(m, replace =T, file = "SI/table_con_5.tex", 
       headers = fe_headers, 
       label = "tab:con_5",
       title = sprintf(ideo_cap, "Frequentist", 6))
```

## Plots

### First Diff Figure

```{r}

plt.tab.FD.bayes %>% 
  ggplot() + 
  geom_pointrange(
    aes(
      x = estimate, y = Outcome,
      xmin = CI_low_95,
      xmax = CI_high_95,
      color = Location), size = .35,
    position = position_dodge(0.5)) +
  geom_linerange(
    aes(
      y = Outcome,
      xmin = CI_low_90,
      xmax = CI_high_90,
      color = Location), size = .7,
    position = position_dodge(0.5)) +
  theme_bw() + 
  theme(text=element_text(size=10),
        axis.title =element_text(size=9)) +
  scale_colour_viridis_d(option = "magma", end =0.8, direction = -1,
                         guide = guide_legend(reverse = TRUE)) +
  geom_vline(xintercept = 0, linetype = "solid") +
  labs(y = "H3: Political Engagement              H2: Rightward Shift       H1: Nativist Backlash",
       color="Location",
       x = "Difference between November 2020 and August 2020 (in SDs)")



ggsave("SI/First_Differences.jpeg", width = 17.8, height = 14, units = "cm")
```
### Figure 1

```{r}
plt.tab.main <- bind_rows("Main Model\n(Bayesian)" = plt.tab.bayes, 
                          "Robustness Checks\n(Frequentist)" = plt.tab.rob,
                          .id = "Framework") %>% 
  mutate(Dataset = fct_rev(fct_inorder(Model))) %>%
  select(estimate, Outcome, CI_low_95, CI_high_95, 
         CI_low_90, CI_high_90, Dataset, Framework)


plt.tab.main %>%  
  ggplot() + 
  geom_pointrange(
    aes(
      x = estimate, y = Outcome,
      xmin = CI_low_95,
      xmax = CI_high_95,
      color = Dataset), size = .35,
    position = position_dodge(0.5)) +
  facet_wrap(~Framework) + 
  geom_linerange(
    aes(
      y = Outcome,
      xmin = CI_low_90,
      xmax = CI_high_90,
      color = Dataset), size = .7,
    position = position_dodge(0.5)) +
  theme_bw() + 
  theme(text=element_text(size=10),
        axis.title =element_text(size=9)) +
  scale_colour_viridis_d(option = "magma", end =0.8, direction = -1,
                         guide = guide_legend(reverse = TRUE)) +
  geom_vline(xintercept = 0, linetype = "solid") +
  geom_vline(xintercept = 0.45, linetype = "dotted") +
  labs(y = "H3: Political Engagement              H2: Rightward Shift       H1: Nativist Backlash",
       color="Data Subset",
       x = "Average Treatment Effect of Attack (in SDs)")

ggsave("figures/Main_Effects.jpeg", width = 17.8, height = 14, units = "cm")
```

### Figure 2

```{r}

bind_rows(party = plt.tab.rep %>%
            mutate(Subgroup = factor(republican,
                                  labels = political_labels)),
          ideology = plt.tab.con %>%
            mutate(Subgroup = factor(conservative,
                                  labels = political_labels)),
          .id = "moderator") %>%
  mutate(Outcome = fct_inorder(Outcome) %>% fct_rev(),
         Subgroup = fct_inorder(Subgroup) %>% fct_rev(),
         moderator = fct_inorder(moderator)) %>%
  ggplot() + geom_pointrange(
    aes(
      x = estimate, y = Outcome,
      xmin = CI_low_95,
      xmax = CI_high_95,
      color = Subgroup), size = .35,
    position = position_dodge(0.5)) +
  facet_wrap(~moderator) + 
  geom_linerange(
    aes(
      y = Outcome,
      xmin = CI_low_90,
      xmax = CI_high_90,
      color = Subgroup), size = .7,
    position = position_dodge(0.5)) +
  theme_bw() + #scale_color_npg() +
  theme(text=element_text(size=10),
        axis.title =element_text(size=9) ) +
  scale_colour_manual(
    values = c("red", "blue"),
    guide = guide_legend(reverse = TRUE)) +
  # scale_colour_viridis_d(option = "magma", end =0.8, direction = -1,
  #                        guide = guide_legend(reverse = TRUE))+
  geom_vline(xintercept = 0, linetype = "solid") +
  labs(y = "H3: Political Engagement      H2: Rightward Shift      H1: Nativist Backlash",
       x = "Conditional Average Treatment Effect of Attack (in SDs)")+
  theme(legend.position= "bottom",
        legend.title=element_text(size = 8,margin = margin(t = 0,b = 0)),
        legend.text = element_text(size = 8,
          margin = margin(t = 0,b = 0, unit = "pt")))
ggsave("figures/Subgroups.jpeg", width = 17.8, height = 13, units = "cm")
```

### Aristotelian Networks

```{r}
source("artistotelian_networks.R")
```


